---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

*Package is work in progress!*

# Introduction
This package parses a git repository history to collect 
comprehensive information about the activity in the repo. The parsed 
data is made available to the user in a tabular format.
To parse the git repo history, use `get_log_regex`.
For each commit, the function also outputs information on which files were changed in a 
nested tibble.

```{r, message=FALSE, warning=FALSE}
library("gitsum")
library("tidyverse")
library("forcats")
```

```{r}
tbl <- get_log_regex() %>%
  select(short_hash, message, total_files_changed, nested)
tbl 
```

```{r}
tbl$nested[[3]]
```

Since the data has such a high resolution, various graphs, tables etc can be 
produced from it to provide insights into the git history.

# Examples
Since the output of `get_log_regex()` is a nested tibble, you can work on it 
as you work on any other tibble.
Let us first have a look at who comitted to this repository:
```{r}
log <- get_log_regex()
log %>%
group_by(author_name) %>%
  count()
```

Next, we want to see which files were contained in most commits:
```{r ggplot1}
log %>%
  unnest(nested) %>% # unnest the tibble
  mutate(changed_file = fct_infreq(changed_file)) %>%
  ggplot(aes(x = changed_file)) + geom_bar() + coord_flip() + 
  theme_minimal()
```

We can also easily get a visual overview of the number of insertions & deletions in commits over time:
```{r ggplot2}
commit.dat <- data.frame(
    edits = rep(c("Insertions", "Deletions"), each = nrow(log)),
    commit = rep(1:nrow(log), 2),
    count = c(log$total_insertions, -log$total_deletions))
    
ggplot(commit.dat, aes(x = commit, y = count, fill = edits)) + 
  geom_bar(stat = "identity", position = "identity") +
  theme_minimal()
```

Or the number of commits broken down by day of the week:
```{r ggplot3}
log %>%
  mutate(weekday = factor(weekday, c("Mon", "Tue", "Wed", "Thu", "Fri", "Sat", "Sun"))) %>% 
  ggplot(aes(x = weekday)) + geom_bar() + 
  theme_minimal()
```
