---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

*Package is work in progress!*

[![Project Status: WIP ? Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](http://www.repostatus.org/badges/latest/wip.svg)](http://www.repostatus.org/#wip)
[![Build Status](https://travis-ci.org/lorenzwalthert/gitsum.svg?branch=master)](https://travis-ci.org/lorenzwalthert/gitsum)
[![codecov](https://codecov.io/gh/lorenzwalthert/gitsum/branch/master/graph/badge.svg)](https://codecov.io/gh/lorenzwalthert/gitsum)


# Introduction
This package parses a git repository history to collect 
comprehensive information about the activity in the repo. The parsed 
data is made available to the user in a tabular format.
To parse the git repo history,use `get_log_regex`.
For each commit, the function also information on which files were changed in a 
nested tibble.

```{r, message=FALSE}
library("gitsum")
library("tidyverse")
library("forcats")
```

```{r}
tbl <- get_log_regex() %>%
  select(short_hash, message, total_files_changed, nested)
tbl 
```
```{r}
tbl$nested[[3]]
```

Since the data has such a high resolution, various graphs, tables ect. 
can be produced from it to give insights into a git history.

# Examples
Since the output of `get_log_regex()` is a nested tibble, you can work on it 
as you work on any other tibble.
Let us first have a look who comitted to this repository:
```{r}
log <- get_log_regex()
log %>%
group_by(author_name) %>%
  count()
```

Next, we want to see which files were contained in most commits.
```{r ggplot1}
log %>%
  unnest(nested) %>% # unnest the tibble
  mutate(changed_file = fct_infreq(changed_file)) %>%
  ggplot(aes(x = changed_file)) + geom_bar() + coord_flip()

```

