---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
library("gitsum")
library("tidyverse")
```

*All just work in progress!*

# Introduction
This package parses a git repository history to collect 
comprehensive information about the activity in the repo. The parsed 
data is made available to the user in a tabular format.
To parse the git repo history, the package contains a function `get_log_regex`
to parse the data via regex
```{r}
get_log_regex()
```

For each commit, it also returns information on which files were changed in a 
nested tibble.

```{r}
tbl <- get_log_regex() %>%
  select(short_hash, message, total_files_changed, nested)
tbl 
```
```{r}
tbl$nested[[3]]
```

Since the data has such a high resolution, various graphs, tables ect. 
can be produced from it to give insights into a git history.

# Examples
Since the output of `get_log_regex()` is a nested tibble, you can work on it 
as you work on any other tibble.
Let us first have a look who comitted to this repository:
```{r}
log <- get_log_regex()
log %>%
group_by(author_name) %>%
  count()
```

Next, we want to see which files were contained in most commits.
```{r}
log %>%
  unnest(nested) %>% # unnest the tibble
  group_by(changed_file) %>%
  count() %>%
  na.omit() %>%
  ggplot(aes(x = changed_file, y = n)) + geom_col() + coord_flip()

```

