---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
library("gitsum")
library("tidyverse")
```

*All just work in progress!*

# Introduction
This package parses a git repository history to collect 
comprehensive information about the activity in the repo. The parsed 
data is made available to the user in a tabular format and can be used to 
create various statistics on the repository. Graphs, figures or even 
reports can be generated automatically.

To parse the git repo history, there are two functions available get_log_simple()`
and `get_log_regex()`
```{r}
get_log_simple()
```

```{r}
get_log_regex()
```

The regex-based function can extract more information. For each commit, 
it also returns information on which files were changed.

```{r}
tbl <- get_log_regex() %>%
  select(short_hash, message, total_files_changed, nested)
tbl 
```
```{r}
tbl$nested[[3]]
```

Since the data has such a high resolution, various graphs, tables ect. 
can be produced from it to give insights into a git history.

# Examples
You can use standard R commands to get your summaries from the commit tibble.
```{r}
log <- get_log_regex()
log %>%
group_by(author_name) %>%
  count()

log %>%
  unnest(nested) %>%
  filter(!is.na(changed_file)) %>%
  ggplot(aes(x = changed_file, y = edits)) + geom_col() + coord_flip()

```

