---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

*Package is work in progress! If you encounter errors / 
problems, please file an issue or make a PR.*

![](https://img.shields.io/badge/lifecycle-maturing-blue.svg)
[![codecov](https://codecov.io/gh/lorenzwalthert/gitsum/branch/master/graph/badge.svg)](https://codecov.io/gh/lorenzwalthert/gitsum)
[![Build Status](https://travis-ci.org/lorenzwalthert/gitsum.svg?branch=master)](https://travis-ci.org/lorenzwalthert/gitsum)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/lorenzwalthert/gitsum?branch=master&svg=true)](https://ci.appveyor.com/project/lorenzwalthert/gitsum)

# Introduction
This package parses a git repository history to collect 
comprehensive information about the activity in the repo. The parsed 
data is made available to the user in a tabular format. The package can also 
generate reports based on the parse data. You can install the development 
version from GitHub.

```{r, eval=FALSE}
remotes::install_github("lorenzwalthert/gitsum")
```

There are two main functions for parsing the history, both return tabular data: 

* `parse_log_simple()` is a relatively fast parser and returns a tibble with 
  one commit per row. There is no file-specific information.
* `parse_log_detailed()` outputs a nested tibble and for each commit, the names
  of the amended files, number of lines changed ect. available. This function
  is slower.

`report_git()` creates a html, pdf, or word report with the parsed log data 
according to a template. Templates can be created by the user or a template 
from the `gitsum` package can be used.

Let's see the package in action.
  
```{r, message=FALSE, warning=FALSE}
library("gitsum")
library("tidyverse")
library("forcats")
```

We can obtain a parsed log like this:

```{r}
tbl <- parse_log_detailed() %>%
  arrange(date) %>%
  select(short_hash, short_message, total_files_changed, nested)
tbl 
```

Since we used `parse_log_detailed()`, there is detailed file-specific
information available for every commit:

```{r}
tbl$nested[[3]]
```

Since the data has such a high resolution, various graphs, tables etc. can be 
produced from it to provide insights into the git history.

# Examples
Since the output of `git_log_detailed()` is a nested tibble, you can work on it 
as you work on any other tibble.
Let us first have a look at who comitted to this repository:
```{r}
log <- parse_log_detailed()
log %>%
group_by(author_name) %>%
  summarize(n = n())
```

We can also investigate how the number of lines of each file in the R 
directory evolved.
```{r per_file, message=FALSE, warning=FALSE}
lines <- log %>%
  unnest()
  add_line_history()

r_files <- grep("^R/", lines$changed_file, value = TRUE)

to_plot <- lines %>%
  filter(changed_file %in% r_files)
ggplot(to_plot, aes(x = date, y = current_lines)) + 
  geom_step() + 
  scale_y_continuous(name = "Number of Lines", limits = c(0, NA)) + 
  facet_wrap(~changed_file, scales = "free_y")
```


Next, we want to see which files were contained in most commits:
```{r ggplot1}
log %>%
  unnest(nested) %>% # unnest the tibble
  mutate(changed_file = fct_lump(fct_infreq(changed_file), n = 10)) %>%
  filter(changed_file != "Other") %>%
  ggplot(aes(x = changed_file)) + geom_bar() + coord_flip() + 
  theme_minimal()
```

We can also easily get a visual overview of the number of insertions & deletions in commits over time:
```{r ggplot2}
commit.dat <- data.frame(
    edits = rep(c("Insertions", "Deletions"), each = nrow(log)),
    commit = rep(1:nrow(log), 2),
    count = c(log$total_insertions, -log$total_deletions))
    
ggplot(commit.dat, aes(x = commit, y = count, fill = edits)) + 
  geom_bar(stat = "identity", position = "identity") +  
  theme_minimal()
```

Or the number of commits broken down by day of the week:
```{r ggplot3}
log %>%
  mutate(weekday = factor(weekday, c("Mon", "Tue", "Wed", "Thu", "Fri", "Sat", "Sun"))) %>% 
  ggplot(aes(x = weekday)) + geom_bar() + 
  theme_minimal()
```
