---
title: "Renaming"
author: "Lorenz Walthert"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Renaming}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

# Input cases

## base case 
Renaming a file in a directory.
```{r}
"R/{rbind.r => bind.r}"
```

A file name change may not have `{` 
```{r}
"API => API2"
```



## add directory in between
rename from vignettes/vagrant-setup.Rmd to vignettes/notes/vagrant-setup.Rmd
```{r}
"vignettes/{ => notes}/mysql-setup.Rmd" 
```



## rename directory
rename from src/dplyr_types.h to inst/include/dplyr_types.h

```{r}
"{src => inst/include}/dplyr_types.h"
```

# Processing

0. Preprocess name to have `{` and `}`.
1. take left title (vignettes / None)
2. take right title (file name)
3. Set left expression in parenthesis as old, right one as new.
4. Paste left title with left expr and right expr and add right title

